Waypoint navigation for an airplane UAV using MAVlink in JdeRobot framework

### 2017-07-07 article/paper.tex
en formato del congreso, añadido algo de estructura

%%%%%%%%%%%%%%%%%%%%% chapter.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% sample chapter
%
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%%%%%%%%%% Springer-Verlag %%%%%%%%%%%%%%%%%%%%%%%%%%
%\motto{Use the template \emph{chapter.tex} to style the various elements of your chapter content.}
\chapter{APM Server Driver}
\label{driver} % Always give a unique label
% use \chaptermark{}
% to alter or adjust the chapter heading in the running head

\abstract*{In order to make accesible to \texttt{JdeRobot} the command sets of \texttt{MAVLink} a driver is needed. \texttt{APM Server driver} ``translates'' the \texttt{JdeRobot} interfaces objects in \texttt{MAVLink} commands an viceversa, giving access to sensors and actuators of the robot. With the typical \texttt{JdeRobot} architecture applications can run in different machines (not necessarily aboard) and can be writen in different programming languages.}

\abstract{In order to make accesible to \texttt{JdeRobot} the command sets of \texttt{MAVLink} a driver is needed. The \texttt{APM Server driver} ``translates'' the \texttt{JdeRobot} interfaces objects in \texttt{MAVLink's} commands an viceversa, giving access to sensors and actuators of the robot. With the typical \texttt{JdeRobot} architecture applications can run in different machines (not necessarily aboard) and can be writen in different programming languages. 
In our case this driver run in a \texttt{Raspberry Pi3} with \texttt{raspbian OS} aboard the plane}

\section{Design}
\label{sec:design}

@@

\begin{itemize}
\item Have to be able to connect to a physical devices like APM 2.8 but as well as to a simutator.
\item Have to access to sensors measures of the aereal robot and interpreting the data and serve its as ICE interfaces objects.
\item Have to be able to recieve incoming commands as ICE interfaces objects and send its to the devices as \texttt{MAVLink's} commands.
\end{itemize}
\begin{figure}[h]
  \centering
  \includegraphics[scale=0.5]{img/diseno.jpg}
  \caption{Diseño de entradas y salidas de \texttt{APM Server}}
  \label{fig:diseno_apms_caja_negra}
\end{figure}

@@

\section{Comunication's layer with APM's devices}
\label{sec:apm_comunication}
% Always give a unique label
% and use \ref{<label>} for cross-references
% and \cite{<label>} for bibliographic references
% use \sectionmark{}
% to alter or adjust the section heading in the running head

@@

\subsection{MAVLink's message}

@@

\subsection{Setup and APM connection}

@@

\subsection{APM data reading}
\label{subsec:apm_data_reading}

@@

\subsection{Sending missions to APM}
\label{sec:mission_apm}

@@

\begin{figure}[H]
  \centering
  \includegraphics[scale=0.70]{img/waypoint-protocol-sendlist.png}
  \caption{\texttt{MAVLink's} missions sending protocol}
  \label{fig:misiones_mavlink}
\end{figure}

\section{JdeRobot's conection layer}
\label{sec:apm_jderobot_comunication}

@@

\section*{Interpretation layer}
\label{interpretation_layer}

@@

\input{referenc}

>>>>

\documentclass{llncs}
\usepackage{makeidx}
\usepackage[utf8]{inputenc}
%\usepackage{graphics}
%\usepackage[pdftex]{graphicx}
\usepackage{listings}
\usepackage{graphicx}

\begin{document}

\title{Waypoint navigation for an airplane UAV using MAVlink in JdeRobot framework}
\author{José Antonio Fernández\inst{1} \and Jose María Cañas Plaza\inst{2}}
\institute{Universidad Rey Juan Carlos}
\titlerunning{Article Abv}
\maketitle

\begin{abstract}
In order to make accesible to \texttt{JdeRobot} the command sets of \texttt{MAVLink} a driver is needed. The \texttt{APM Server driver} ``translates'' the \texttt{JdeRobot} interfaces objects in \texttt{MAVLink's} commands an viceversa, giving access to sensors and actuators of the robot. With the typical \texttt{JdeRobot} architecture applications can run in different machines (not necessarily aboard) and can be writen in different programming languages. 
In our case this driver run in a \texttt{Raspberry Pi3} with \texttt{raspbian OS} aboard the plane
\end{abstract}

\section{Introduction}

%MAVlink protocol

\section{UAV support in JdeRobot}

\section{MAVlink protocol}

\section{APM driver in JdeRobot}

\subsection{Design}
\label{sec:design}

@@

\begin{itemize}
\item Have to be able to connect to a physical devices like APM 2.8 but as well as to a simutator.
\item Have to access to sensors measures of the aereal robot and interpreting the data and serve its as ICE interfaces objects.
\item Have to be able to recieve incoming commands as ICE interfaces objects and send its to the devices as \texttt{MAVLink's} commands.
\end{itemize}

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.5]{img/diseno.jpg}
  \caption{Diseño de entradas y salidas de \texttt{APM Server}}
  \label{fig:diseno_apms_caja_negra}
\end{figure}

@@

\subsection{Comunication with APM devices layer}
\label{sec:apm_comunication}
% Always give a unique label
% and use \ref{<label>} for cross-references
% and \cite{<label>} for bibliographic references
% use \sectionmark{}
% to alter or adjust the section heading in the running head

@@

\subsubsection{MAVLink's message}

@@

\subsubsection{Setup and APM connection}

@@

\subsubsection{APM data reading}
\label{subsec:apm_data_reading}

@@

\subsubsection{Sending missions to APM}
\label{sec:mission_apm}

@@

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.70]{img/waypoint-protocol-sendlist.png}
  \caption{\texttt{MAVLink's} missions sending protocol}
  \label{fig:misiones_mavlink}
\end{figure}

\subsection{Connection to applications layer}
\label{sec:apm_jderobot_comunication}

@@

\subsection{Interpretation layer}
\label{interpretation_layer}

@@

\section{UAV Commander application}

\section{Conclusions}

\end{document}
